MNRAS \LaTeXe\ template -- title goes here

### 2018-06-13 paper_mnras/paper.tex
default is to turn newtxtext on
mnras template works on astrohub.uvic.ca
add color to comment

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
% \usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

% for author's comments; choose your own color and replace 'fh' and
% 'FH' with your name and initials
\newcommand{\fhcom}[1]{\shortcomment{PineGreen}{FH}{#1}}

@@

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \lFig{mass-N14}
\end{figure}

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

% for author's comments; choose your own color and replace 'fh' and
% 'FH' with your name and initials
\usepackage[usenames,dvipsnames]{color}
\usepackage[]{color}
\newcommand{\fhcom}[1]{{\color{PineGreen}[\emph{FH: #1}]}}
\newcommand{\fhtxt}[1]{{\color{PineGreen}[FH: #1]}}

@@

% Example figure
\begin{figure}
  % To include a figure from a file named example.*
  % Allowable file formats are eps or ps if compiling using latex
  % or pdf, png, jpg if compiling using pdflatex

  %\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
  \caption{This is an example figure. Captions appear below each
    figure.  Give enough detail for the reader to understand what
    they're looking at, but leave detailed discussion to the main body
    of the text.  This particular figure file will appear when you
    exectute the example notebook in
    \texttt{figs/figure\_template}. Then uncomment the
    \texttt{includegraphics} command in the latex source file.} 
    \lFig{mass-N14}
\end{figure}
